### 2023-01-04 elsman/manuscript.tex
WFS edits

Take for example the AFI framework, containing one symmetry distinct T-site. AFI contains 4-, 6-, 12-, and 14-MRs. To describe that T-site we can count how many of each of those rings pass through the T-site. We can also prune this list using our modified definition of a shortcut, the shortest path rings definition \cite{sastre-topological-2009}, or the rings contained within the vertex symbol of this T-site \cite{okeeffe-vertex-1997}. Using the ring index outlined above, each of these conventions will provide a different description of the zeolite (highlighted in \cref{fig:afi-funnel}):
\begin{itemize}
\item Rings: 4\(\cdot\)6\(_{\text{13}} \cdot\)12\(\cdot\)14\(_{\text{7}}\)
\item This work: 4\(\cdot\)6\(_{\text{13}} \cdot\)12
\item Shortest Path Rings: 4\(\cdot\)6\(_{\text{13}}\)
\item Vertex Symbol Rings: 4\(\cdot\)6\(_{\text{11}}\)
\end{itemize}

\begin{figure}
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figures/chapter-3/afi-funnel.pdf}
\caption{Diagram shwoing the ring counts of each size ring that pass through the single symmetry distinct T-site in AFI for each of the various ring finding conventions. \label{fig:afi-funnel}}
\end{figure}
\end{figure}

>>>>

Take for example the AFI framework, containing one symmetry distinct T-site. AFI contains 4-, 6-, 12-, and 14-MRs. To describe that T-site we can count how many of each of those rings pass through the T-site. We can also prune this list using our modified definition of a shortcut, the shortest path rings definition \cite{sastre-topological-2009}, or the rings contained within the vertex symbol of this T-site \cite{okeeffe-vertex-1997}. Using the ring index outlined above, each of these conventions will provide a different description of the zeolite (highlighted in \cref{fig:afi-funnel}):
\begin{itemize}
\item Rings: 4\(\cdot\)6\(_{\text{13}} \cdot\)12\(\cdot\)14\(_{\text{7}}\)
\item Modified Shortcut Rings: 4\(\cdot\)6\(_{\text{13}} \cdot\)12
\item Shortest Path Rings: 4\(\cdot\)6\(_{\text{13}}\)
\item Vertex Symbol Rings: 4\(\cdot\)6\(_{\text{11}}\)
\end{itemize}

\begin{figure}
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figures/chapter-3/afi-funnel.pdf}
\caption{Diagram showing the ring counts of each size ring that pass through the single symmetry distinct T-site in AFI for each of the various ring finding conventions. \label{fig:afi-funnel}}
\end{figure}
\end{figure}
